---
title: "Fake News Classification EDA Notebook"
output: html_notebook
---

# Perform EDA on News Dataset that includes stories from the Guardian

# Imports and Constants
```{r}
library(dplyr)
library(readr)
library(ggplot2)

DATA_PATH = '../data/'
PRE_PROCESSED_DATA_FILE_NAME = 'news_dataset_pre_processed.csv'
GUARDIAN_DATA_FILE_NAME = 'guardian_news_dataset_cleaned.csv'
RANDOM_STATE = 42
```

# Load Data
```{r}
df <- read_csv(paste(DATA_PATH, PRE_PROCESSED_DATA_FILE_NAME, sep='')) %>%
  select(title, text, label, clean_text_tokens, clean_title_tokens)

df_guard <- read_csv(paste(DATA_PATH, GUARDIAN_DATA_FILE_NAME, sep=''))
```
# Integrate Guardian Stories into the Dataset as true
## Split original data by label
```{r}
df_fake <- filter(df, label == 'fake')
df_true <- filter(df, label == 'true')
```
There are `r nrow(df_fake)` fake news stories.
Half that amount of true stories from the Guardian will be integrated into the set of true news stories.
## Take a random sample of the original true news stories
```{r}
set.seed(RANDOM_STATE)
df_true_sample = sample_n(df_true, 8724)
```
## Take a random sample of the Guardian news stories
```{r}
set.seed(RANDOM_STATE)
df_guard_sample <- sample_n(df_guard, 8723)
```
### Assign the label true
```{r}
df_guard_sample <- mutate(df_guard_sample, label = 'true') 
```
## Make column names consistent
```{r}
df_guard_sample <- df_guard_sample %>%
  rename(title = webTitle,
         text = fields.bodyText
         )
```
## Combine Dataframes for analysis
```{r}
df_combined <- bind_rows(select(df_fake, title, text, label),
                         select(df_true_sample, title, text, label),
                         select(df_guard_sample, title, text, label))
```


